Reliability of stock-recruitment function estimation in state space assessment models

### 2023-09-29 Ecov_study/recruitment_functions/paper/main.tex

@@

>>>>

%%--ANALYSIS--%%
\subsubsection*{Analysis}

Metrics of interest: 
\begin{enumerate}
    \item Ability to correctly identify a stock recruitment relationship
    \item Ability correctly identify the functional form of the stock recruitment relationship
    \item Differences in estimation error (SSB, R) when SR relationships are correctly/incorrectly identified
\end{enumerate}

Generalized linear models

Generalized linear mixed models

Classification trees

@@

\begin{figure}[htb]
\begin{center}
\includegraphics[width = 6in]{dRdX_1RdRdx.pdf}
\caption{Sensitivity of recruitment to environmental covariates for the three functional forms considered in this study.}
\end{center}
\end{figure}

\begin{figure}[htb]
\begin{center}
\includegraphics[width = 5in]{raw_boxplots_SR.pdf}
\caption{Model selection results for whether a stock recruitment relationship was correctly identified, expressed as marginal proportions against individual covariates.}
\end{center}
\end{figure}

\begin{figure}[htb]
\begin{center}
\includegraphics[width = 5in]{raw_boxplots_form.pdf}
\caption{Model selection results for whether the correct stock recruitment functional form was identified, expressed as marginal proportions against individual covariates.}
\end{center}
\end{figure}

\begin{figure}[htb]
\begin{center}
\includegraphics[width = 6in]{effect_size_glm_glmm.pdf}
\caption{Effect sizes for predicting estimated via a binomial generalized linear model and a binomial generalized linear mixed model with simulation random number seed as a random intercept.}
\end{center}
\end{figure}

\begin{figure}[htb]
\begin{center}
\includegraphics[width = 5in]{reg_tree.pdf}
\caption{Classification tree analysis of model selection results. R package `rpart' was used for the model fit and visualization. Following default settings in rpart, the complexity parameter is set at $c_p=0.01$ which represents the minimum classification improvement required for any split.}
\end{center}
\end{figure}
